A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-08-10 paper/elsarticle/elsarticle-template.tex
paper

Correcting for projective distortions of the sort outlined in Section~\ref{sec:intro} can be achieved by modeling the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene (i.e., by `calibrating' the projector) and the geometry of the scene itself (i.e., by recovering the scene plane relative to the projector) within at least the projector's field of view. This is because the scene point `illuminated' by a pixel in the projector's image plane can be recovered by intersecting its corresponding ray with the geometry of the scene surface. To model this interaction, we (i) carry out a one-time projector calibration, which in our approach calls for additionally calibrating a camera facing downwards to the scene plane and includes recovery of the scene plane as a convenient side effect. Next, we use the relative camera-projector-scene plane geometry to (ii) compute a plane-induced homography that warps the image to be projected in a manner that it appear undistorted to the viewer, and placed in alignment with the axes of a proxy image of the scene. These two points are treated in Sections~\ref{sec:approach:geometry} and \ref{sec:approach:homography}, respectively.

@@

\section{Evaluation}

@@

We evaluate our approach by using a 960 pixel~$\times$~600 pixel image of the TU Wien logo (cf.\ Figure \ref{fig:warp}) to augment 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Wien, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same metric dimensions of 50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~$\times$~600; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis if aspect ratio is to be preserved.}. All experiments were carried out by the same technician, experienced in both approaches.

@@

\begin{table}[ht]
\caption{Deviations in measured angles from $90^\circ{}$ across the 15 augmentations produced using our approach.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.4cm}{r p{1.75cm} p{1.75cm}}
\toprule
  & Top Right & Bottom Left\\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}

>>>>

Correcting for projective distortions of the sort outlined in Section~\ref{sec:intro} can be achieved by modeling the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene (i.e., by `calibrating' the projector) and the geometry of the scene itself (i.e., by recovering the scene plane relative to the projector) within at least the projector's field of view. This is because the scene point `illuminated' by a pixel in the projector's image plane can be recovered by intersecting its corresponding ray with the geometry of the scene surface; modeling the geometry that relates projector and scene plane thus enables one to reason about the problem of correcting for distortions in terms of geometry. To model this interaction, we (i) carry out a one-time projector calibration, which in our approach calls for additionally calibrating a camera facing downwards to the scene plane and includes recovery of the scene plane as a convenient side effect. Next, we use the relative camera-projector-scene plane geometry to (ii) compute a plane-induced homography that warps the image to be projected in a manner that it appear undistorted to the viewer, and placed in alignment with the axes of a proxy image of the scene. These two points are treated in Sections~\ref{sec:approach:geometry} and \ref{sec:approach:homography}, respectively.

@@

@@

\section{Evaluation}
We evaluate our approach by using a 960 pixel~$\times$~600 pixel image of the TU Wien logo (cf.\ Figure \ref{fig:warp}) to augment 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Wien, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same metric dimensions of 50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~$\times$~600; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis if aspect ratio is to be preserved.}. All experiments were carried out by the same technician, experienced in both approaches.

@@

\begin{table}[ht]
\caption{Deviations in measured angles from $90^\circ{}$ across the 15 augmentations produced using our approach.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.25cm}{r p{1.725cm} p{1.725cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}
